Predicting virus-receptor mutant binding by molecular dynamics simulation

### 2013-07-19 paper.tex
Submitted version to JCTC.

\clearpage
\begin {table}[H]
\caption{\label{tab:summary_mutants}Summary of prior information available for each mutation tested. Observed $in~vivo$ refers to mutations that have been observed in rodent populations. Phenotype $in~vitro$ refers to the observed phenotype in $in~vitro$ viral entry assays.} 
\begin{center}
  \resizebox{11cm}{!} {
    \begin{tabular}{l c r r}
    \hline
      Mutation & Observed $in~vivo$ & Phenotype $in~vitro$ \\
            WT &                Yes &         Normal Entry \\
         N348A &                 No &                    - \\
         N348K &                Yes &     Diminished Entry \\
         N348W &                 No &                    - \\
         Y211A &                 No &        No Expression \\
         Y211D &                Yes &        No Expression \\
         Y211T &                 No &     Diminished Entry \\
        vR111A &                 No &     Diminished Entry \\
   N348A/Y211A &                 No &                    - \\
   N348W/Y211A &                 No &                    - \\
  vR111A/Y211A &                 No &                    - \\
    \hline
    \end{tabular}
  }
\end{center}
\end{table}

>>>>

\clearpage
\begin {table}[H]
\caption{\label{tab:summary_mutants}Summary of prior information available for each mutation tested. Observed $in~vivo$ refers to mutations that have been observed in rodent populations. Phenotype $in~vitro$ refers to the observed phenotype in $in~vitro$ viral entry assays.} 
\begin{center}
  \resizebox{11cm}{!} {
    \begin{tabular}{l c r r}
    \hline
      Mutation & Observed $in~vivo$ & Phenotype $in~vitro$ \\ \hline
            WT &                Yes &         Normal Entry \\
         N348A &                 No &                    - \\
         N348K &                Yes &     Diminished Entry \\
         N348W &                 No &                    - \\
         Y211A &                 No &        No Expression \\
         Y211D &                Yes &        No Expression \\
         Y211T &                 No &     Diminished Entry \\
        vR111A &                 No &     Diminished Entry \\
   N348A/Y211A &                 No &                    - \\
   N348W/Y211A &                 No &                    - \\
  vR111A/Y211A &                 No &                    - \\
    \hline
    \end{tabular}
  }
\end{center}
\end{table}
